---
title: "Leaflet Deliverable"
author: "Martín Dévora Pajares"
date: "1 de junio de 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Leaflet Deliverable

Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

```{r cars}
library(leaflet)
```

## Creating data to be plotted

We will present the list of the seven greatest asteroid impact craters in the Earth, plotting them in a world map and printing circles around their impact place according to their diameters.

```{r echo=FALSE}
crater_list <-data.frame(name = c("Vredefort", "Sudbury", "Chicxulub", "Popigai", "Manicouagan", "Acraman", "Morokweng"),
                         wiki = c("https://en.wikipedia.org/wiki/Vredefort_crater", "https://en.wikipedia.org/wiki/Sudbury_Basin", "https://en.wikipedia.org/wiki/Chicxulub_crater", "https://en.wikipedia.org/wiki/Popigai_crater", "https://en.wikipedia.org/wiki/Manicouagan_Reservoir", "https://en.wikipedia.org/wiki/Acraman_crater", "https://en.wikipedia.org/wiki/Morokweng_crater"),
                         crater_size = c(300, 250, 180, 100, 100, 90, 70),
                         lat = c(-27, 46.36, 21.20, 71.39, 51.23, -32.1, -26.28),
                         lng = c(27.30, -81.11, -89.30, 111.11, -68.42, 135.27, 23.32))
```

## Plotting craters given sizes
```{r echo=FALSE}
crater_list %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 4, radius = crater_list$crater_size * 1000, color = c('red'), popup = sprintf("Name: %s, Size (km): %s, More info: %s",crater_list$name,crater_list$crater_size, crater_list$wiki))
```
